---
title: "Supplementary Material for 'Marine trophic network analysis and its potential resilience in the Strait of Magellan'"
# author: Claudia Andrade^1^*, Taryn Sepúlveda^1^, Cristóbal Rivera^1^, Cristian Aldea^2^ & Tomás I. Marina^3^
# date: 1. Laboratorio de Ecología Funcional, Universidad de Magallanes, Punta Arenas, Chile. \newline 2. Centro de Investigación GAIA Antártica and Departamento de Ciencias y Recursos Naturales, Universidad de Magallanes, Punta Arenas, Chile. \newline 3. Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina. \newline *Corresponding author (claudia.andrade@umag.cl)
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
#classoption: landscape
#bibliography: AMPYaganes.bib
csl: "elsevier-harvard2.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{amsmath}
- \usepackage{pdflscape,booktabs}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \pagenumbering{gobble}
---

The following tables summarise the data and results related to the study of the network of trophic (predator-prey) interactions, food web, for the Strait of Magellan ecosystem.

Table 1 is the complete list of trophic interactions and references that confirm each of them.

Table 2 shows the results for the small-world pattern analysis, following Marina et al. (2018) (https://doi.org/10.1371/journal.pone.0198217).

Table 3 is the species list with details on trophic species cases (aggregated taxa) and its properties (e.g. degree, closeness, betweenness, Keystone Species Index -KSI-, trophic position, and topological role).

Table 4 shows the results of the cumulative degree distribution fit of the food web.

\newpage
\blandscape

```{r tableS1, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load packages
require(tidyverse)
require(knitr)
require(dplyr)
require(kableExtra)
require(pander)

# Load data
int_list <- read.csv(file = "../Data/InteractionList_Magellan_220825.csv", header = TRUE)

# Filter interaction list
int_tbl <- int_list %>% 
  dplyr::select(-c(Taxonomic_group_prey, Taxonomic_group_pred)) %>% 
  rename(Link = Full_reference, Reference = Citation) %>% 
  distinct(Prey, Predator, .keep_all = TRUE)

# Table S1
pandoc.table(int_tbl %>% arrange(., (Predator)) %>% 
               mutate(ID = paste('\\tiny', ID), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator), Reference = paste('\\tiny', Reference), Link = paste('\\tiny', Link)), style="multiline", split.tables = Inf, justify = c("left","left","left","left","right"),
             caption = "List of predator-prey (trophic) interactions used to build the food web of the Strait of Magellan. References and link to them (Link) are provided for each interaction.")

```

\elandscape
\newpage

```{r tableS2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load data
load("../Results/Network&SpProps_22mar25.rda")

# Table S3
rownames(datos_sw) <- c()
pandoc.table(datos_sw %>%
               dplyr::select(da.PathLength, da.Clustering, da.CPlow, da.CPhigh, da.CClow, da.CChigh, da.isSW) %>% 
               mutate_at(vars(as.numeric()), round, 4) %>% 
               rename("EmpPL"="da.PathLength", "EmpCC"="da.Clustering", "RndPLLow"="da.CPlow", "RndPLUp"="da.CPhigh", "RndCCLow"="da.CClow", "RndCCUp"="da.CChigh", "SW"="da.isSW"), style="multiline", split.tables = Inf, justify = c("left","left","left","left","left","left","center"),
             caption = "Results of the small-world fit after comparing empirical and random Path Length and Clustering Coefficient properties. 1000 random networks were built for comparison with the empirical case. EmpPL: Empirical Path Length; EmpCC: Empirical Clustering Coefficient; RndPLLow: Path Length confidence interval lower limit for random networks; RndPLUp: Path Length confidence interval upper limit for random networks; RndCCLow: Clustering Coefficient confidence interval lower limit for random networks; RndCCUp: Clustering Coefficient confidence interval upper limit for random networks. Note that the empirical path length (EmpPL) is shorter than the confidence interval for its random counterpart (RndPLLow-RndPLUp) and the empirical clustering coefficient (EmpCC) is greater than the confidence interval for its random counterpart (RndCCLow-RndCCUp).")

```

\blandscape
\newpage

```{r tableS3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load data
load("../Results/AllSpProps_24mar25.rda")

# Table S2
pandoc.table(all_sp_prop %>% arrange(., (Keystone_rank)) %>% 
               mutate_at(vars(TL), round, 2) %>% 
               mutate_at(vars(Closeness, Between), round, 4) %>% 
               dplyr::select(TrophicSpecies, Group, NumPrey, NumPred, TotalDegree, Closeness, Between,
                             TL, TopRole, Keystone_rank) %>% 
               rename("Trophic species"="TrophicSpecies", "Betweeness"="Between", "TP"="TL", "KSI rank"="Keystone_rank"), style="multiline", split.tables = Inf, justify = c("left", "left","center","center","center","center","center","center","center","center"),
             caption = "List of species, including  node-level properties, for the food web of the Strait of Magellan. NumPrey: Number of prey; NumPred: Number of predators; TP: trophic position; TopRole: Topological role, where 'hubcon' = network connector, 'modcon' = module connector, 'modhub' = module hub, and 'modspe' = module specialist; KSI rank: Keystone Species Index ranking.")

```

\elandscape
\newpage

```{r tableS4, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load data
load("../Results/Network&SpProps_22mar25.rda")

# Table S4
pandoc.table(m_dd$models %>%
               arrange(., (AIC)) %>%
               dplyr::select(AIC, BIC, family, model) %>%
               rename("Model"="model", "Model family"="family"), style="multiline", split.tables = Inf, justify = c("left","left","left","left"),
             caption = "Results of the degree distribution fit. Exponential and power law model families were tested, and AIC (Akaike Information Criterion) and BIC (Bayesian Information Criterion) were used to select the best fit (i.e., lower AIC and BIC). The exponential model is the best fit.")

```
